---
title: An R Markdown document converted from "proj1_s_v2.ipynb"
output: html_document
---

<h2> <span style="color: Maroon;"> UniMi | SL | Supervised Learning | Stats'N'Facts </span> </h2>

## <span style="color: Blue;"> 0. Outline [TODO] </span>

## <span style="color: IndianRed;"> 1. Notebook Setup </span>

### <span style="color: LightSalmon;"> *1.1 Load Required Libraries* </span>

```{r}
library(MASS)
library(ggpubr)
library(olsrr)
library(dplyr)
library(purrr)
library (DescTools)
library(gplots)
library(car)
library(Hmisc)
library(PerformanceAnalytics)
library(olsrr)
library(ISLR)
library(rpart)
library(rpart.plot)
library(party)
library("partykit")
library(caTools)
library(caret)
library(randomForest)
library(ranger)
```

### <span style="color: LightSalmon;"> *1.2 Load Dataset* </span>

```{r}
carRentals <-  read.csv(file='CarRentalDataV1.csv', stringsAsFactors=TRUE)
```

### <span style="color: LightSalmon;"> *1.3 Data Description* **[TODO]** </span>

### <span style="color: LightSalmon;"> *1.4 User-defined Functions* **[TODO]** </span>

```{r}
mse.usd <- function(model){
    mean(exp(model$residuals)^2)
}
```

```{r}
mae.usd <- function(model){
    mean(abs(exp(model$residuals)))
}
```

## <span style="color: IndianRed;"> 2. Exploratory Data Analysis </span>

### <span style="color: LightSalmon;"> 2.1 Initial Overall Exploration </span>

```{r}
names(carRentals)
```

```{r}
head(carRentals)
```

```{r}
str(carRentals)
```

**Correlations of Numeric Features**

```{r}
cR.numeric <-carRentals %>% select(rate.daily, vehicle.year, rating, reviewCount, renterTripsTaken)
rcorr(as.matrix(cR.numeric))
```

```{r}
scatterplotMatrix(cR.numeric, regLine=TRUE)
```

```{r}
chart.Correlation(cR.numeric, histogram=TRUE, pch=19)
```

### <span style="color: LightSalmon;"> 2.2 Exploration of Dependent Variable: rate.daily </span>

#### <span style="color: #FFBF00;"> *2.2.1 Overall Assessment of rate.daily* </span>

**Summary of dependent variable**

```{r}
summary(carRentals$rate.daily)
```

It appears that our dependent variable suffers from:
* Non-Normality: Mean is almost 50% larger than median
* Severe Outliers: Max rate is 21 IQR's away from 3rd Qu.

**Normality Test**

```{r}
options(repr.plot.width=4, repr.plot.height=3)
```

```{r}
ggqqplot(carRentals$rate.daily)
```

```{r}
ggdensity(carRentals, x="rate.daily", fill="lightgray", title="rate.daily") +
  stat_overlay_normal_density(color="red", linetype="dashed")
```

```{r}
hist(carRentals$rate.daily, breaks=sqrt(nrow(carRentals)))
```

Attempting to use Logarithm to improve normality

```{r}
carRentals$log.rate.daily <- log(carRentals$rate.daily)
```

```{r}
summary(carRentals$log.rate.daily)
```

```{r}
ggqqplot(carRentals$log.rate.daily)
```

```{r}
ggdensity(carRentals, x="log.rate.daily", fill="lightgray", title="log.rate.daily") +
  stat_overlay_normal_density(color="red", linetype="dashed")
```

```{r}
options(repr.plot.width=8, repr.plot.height=4)
```

```{r}
par(mfrow=c(1,2))
hist(carRentals$rate.daily, main="rate.daily", breaks=sqrt(nrow(carRentals)))
hist(carRentals$log.rate.daily, main="log.rate.daily", breaks=sqrt(nrow(carRentals)))
```

#### <span style="color: #FFBF00;"> *2.2.2 Handling Outliers of rate.daily* </span>

**Outliers of rate.daily**

```{r}
cutoff.mult <- 2
```

```{r}
uq <- quantile(carRentals$rate.daily, .75)
lq <- quantile(carRentals$rate.daily, .25)
iqr <- uq - lq
outlier.upper.cutoff <- uq + cutoff.mult * iqr
```

```{r}
nrow(carRentals[carRentals$rate.daily > outlier.upper.cutoff,])
```

**Outliers of log.rate.daily**

```{r}
uq <- quantile(carRentals$log.rate.daily, .75)
lq <- quantile(carRentals$log.rate.daily, .25)
iqr <- uq - lq
outlier.upper.cutoff <- uq + cutoff.mult * iqr
```

```{r}
nrow(carRentals[carRentals$log.rate.daily > outlier.upper.cutoff,])
```

```{r}
print(summary(carRentals[carRentals$log.rate.daily > outlier.upper.cutoff,]$fuelType))
```

```{r}
print(summary(carRentals[carRentals$log.rate.daily > outlier.upper.cutoff,]$vehicle.year))
```

Very few rental cars are classical from the last century, *which likely have a different pricing mechanism than the bulk of rental cars*

```{r}
carRentals[carRentals$vehicle.year < (2012-cutoff.mult*(2019-2012)),]$vehicle.year
```

**Exploring the remaining outliers of log.rate.daily which are not classical cars**

```{r}
carRentals[carRentals$log.rate.daily > outlier.upper.cutoff & carRentals$vehicle.year > (2012-cutoff.mult*(2019-2012)),]
```

```{r}
unique(carRentals[carRentals$log.rate.daily > outlier.upper.cutoff & carRentals$vehicle.year > (2012-cutoff.mult*(2019-2012)),]$vehicle.make)
```

It appears that most current rental cars with outlier log.rate.daily are legitimate data points of fancier car models

### <span style="color: LightSalmon;"> 2.3 Relations to Numerical Features </span>

#### <span style="color: #FFBF00;"> *2.3.1 Relationship of rate.day ~ vehicle.year* </span>

```{r}
lm.fit <- lm(log.rate.daily ~ vehicle.year, data=carRentals)
summary(lm.fit)
```

```{r}
mse.usd(lm.fit)
```

```{r}
options(repr.plot.width=7, repr.plot.height=5)
```

```{r}
plot(log.rate.daily ~ vehicle.year, pch=19, data=carRentals)
abline(lm.fit, col="red", lwd=3)
```

**Dropping classical cars outliers**

```{r}
cutoff.mult <- 3
uq <- quantile(carRentals$vehicle.year, .75)
lq <- quantile(carRentals$vehicle.year, .25)
iqr <- uq - lq
outlier.lower.cutoff <- lq - cutoff.mult * iqr
```

```{r}
outlier.lower.cutoff
```

```{r}
classical.rows <- as.numeric(rownames(carRentals[carRentals$vehicle.year < outlier.lower.cutoff,]))
```

```{r}
carRentals[classical.rows,]
```

```{r}
carRentals.noClassical <- carRentals[-classical.rows,]
lm.fit <- lm(log.rate.daily ~ vehicle.year, data=carRentals.noClassical)
summary(lm.fit)
```

```{r}
mse.usd(lm.fit)
```

```{r}
plot(log.rate.daily ~ vehicle.year, pch=19, data=carRentals.noClassical)
abline(lm.fit, col="red", lwd=3)
```

Classical car rentals likely have a different market than regular rental cars. Also, their sample size is small in this dataset. <br>
By dropping the classical car outliers, the adjusted R<sup>2</sup> increased (0.08 vs 0.03) and the estimates for the intercept and year have changed significantly

#### <span style="color: #FFBF00;"> *2.3.2 Relationship of log.rate.daily ~ rating and review count* </span>

```{r}
sum(is.na(carRentals.noClassical$rating))
```

```{r}
carRentals.noClassical[is.na(carRentals.noClassical$rating) & carRentals.noClassical$renterTripsTaken != 0,]
```

All rating entries with NA are for cars which have 0 reviews, so this is a logical non-existance of data rather than a missing values problem

```{r}
lm.fit <- lm(log.rate.daily ~ reviewCount, data=carRentals.noClassical)
summary(lm.fit)
```

```{r}
mse.usd(lm.fit)
```

```{r}
lm.fit <- lm(log.rate.daily ~ rating + reviewCount, data=carRentals.noClassical)
summary(lm.fit)
```

```{r}
mse.usd(lm.fit)
```

```{r}
options(repr.plot.width=12, repr.plot.height=5)
par(mfrow=c(1,2))

plot(log.rate.daily ~ rating, pch=19, data=carRentals.noClassical)
abline(lm(log.rate.daily ~ rating, data=carRentals.noClassical), col="red", lwd=3)

plot(log.rate.daily ~ reviewCount, pch=19, data=carRentals.noClassical)
abline(lm(log.rate.daily ~ reviewCount, data=carRentals.noClassical), col="red", lwd=3)
```

**Explore the negative trend between reviewCount and log.rate.daily (*middle graph*)**

```{r}
lm.fit <- lm(reviewCount ~ vehicle.year + rating, data=carRentals.noClassical)
summary(lm.fit)
```

```{r}
mse.usd(lm.fit)
```

```{r}
options(repr.plot.width=5, repr.plot.height=5)
plot(reviewCount ~ vehicle.year, pch=1, data=carRentals.noClassical)
abline(lm(reviewCount ~ vehicle.year, data=carRentals.noClassical), col="red", lwd=3)
```

Counterintuitively, the more reviews the lower the rate. <br> Part of this could be attributed to older cars accumulating more reviews (*negative correlation of reviewCounts with vehicle.year)*

#### <span style="color: #FFBF00;"> *2.3.2 Relationship of log.rate.daily ~ renterTripsTaken* </span>

```{r}
summary(carRentals.noClassical$renterTripsTaken)
```

```{r}
hist(carRentals.noClassical$renterTripsTaken, breaks=sqrt(nrow(carRentals.noClassical)))
```

```{r}
zero.renterTripsTaken <- carRentals.noClassical[carRentals.noClassical$renterTripsTaken == 0,]
```

```{r}
options(repr.plot.width=8, repr.plot.height=4)
par(mfrow=c(1,2))
hist(zero.renterTripsTaken$vehicle.year, breaks= (max(zero.renterTripsTaken$vehicle.year)-min(zero.renterTripsTaken$vehicle.year)+1))
hist(carRentals.noClassical$vehicle.year, breaks= (max(carRentals.noClassical$vehicle.year)-min(carRentals.noClassical$vehicle.year)+1))
```

**Check ratio of zero trips per stock of cars for each year**

```{r}
count.rows.perYear <- as.data.frame(table(zero.renterTripsTaken$vehicle.year))
zero.renterTripsTaken.perYear <- as.data.frame(table(carRentals.noClassical$vehicle.year))
df12 <- left_join(zero.renterTripsTaken.perYear, count.rows.perYear, by = 'Var1')
df12$ratio.zeroTrips.perYear <- df12$Freq.y / df12$Freq.x
df12 <- df12[-c(1:4),]
```

```{r}
options(repr.plot.width=5, repr.plot.height=5)
plot(x=df12$Var1, y=df12$ratio.zeroTrips.perYear, data=df12)
```

```{r}
count.renterTripsTaken <- carRentals.noClassical %>% count(renterTripsTaken)
```

```{r}
summary(count.renterTripsTaken)
```

**Distribution of "Count" of renterTripsTaken**

```{r}
hist(count.renterTripsTaken$n, breaks=80)
```

```{r}
carRentals.noClassical[carRentals.noClassical$renterTripsTaken == 0,]
```

**Regression on renterTripsTaken (as-is)**

```{r}
lm.fit <- lm(log.rate.daily ~ renterTripsTaken, data=carRentals.noClassical)
summary(lm.fit)
```

```{r}
mse.usd(lm.fit)
```

```{r}
plot(log.rate.daily ~ renterTripsTaken, pch=19, data=carRentals.noClassical)
abline(lm.fit, col="red", lwd=3)
```

**Regression on renterTripsTaken (dropped rows with 0 trips prior to 2020)**

```{r}
cutoffYear.zeroTrips <- 2020
lm.fit <- lm(log.rate.daily ~ renterTripsTaken, data=carRentals.noClassical[(carRentals.noClassical$renterTripsTaken != 0 & carRentals.noClassical$vehicle.year < cutoffYear.zeroTrips) | carRentals.noClassical$vehicle.year >= cutoffYear.zeroTrips,])
summary(lm.fit)
```

No rows are dropped based on number of taken trips

```{r}
mse.usd(lm.fit)
```

### <span style="color: LightSalmon;"> 2.4 Relations to Categorical Features </span>

#### <span style="color: #FFBF00;"> *2.4.1 Relationship of log.rate.daily ~ vehicle.make* </span>

##### <span style="color: Teal;"> *2.4.1.1 Problems with vehicle.make data* </span>

**Concilliation of Multi-spelled brands**

Brand variable requires consolidation if it is to be used properly.

```{r}
carRentals.noClassical %>% count(vehicle.make)
```

##### <span style="color: Teal;"> *2.4.1.2 Reconciliation of multi-spelled car makes with the most commonly spelled version* </span>

```{r}
makes.to.change <- c("Alfa-romeo", "INFINITI", "Mercedes-benz")
makes.references <- c("Alfa Romeo", "Infiniti", "Mercedes-Benz")
```

```{r}
for(i in 1:length(makes.to.change)) {
  makes.to.change.rows <- carRentals.noClassical[carRentals.noClassical$vehicle.make == makes.to.change[i],]
  for(j in 1:nrow(makes.to.change.rows)) {
    row.temp <- makes.to.change.rows[j,]
    carRentals.noClassical[row.names(row.temp), "vehicle.make"] <- makes.references[i]
  }
}
```

Confirm successful reconciliation of makes

```{r}
carRentals.noClassical %>% count(vehicle.make)
```

Reset factors

```{r}
carRentals.noClassical$vehicle.make <- droplevels(carRentals.noClassical$vehicle.make)
```

```{r}
table(carRentals.noClassical$vehicle.make)
```

```{r}
options(repr.plot.width=15, repr.plot.height=10)
par(mfrow=c(2,1))
boxplot(carRentals.noClassical$log.rate.daily ~ vehicle.make, data=carRentals.noClassical, las=2)
plotmeans(log.rate.daily ~ vehicle.make, data=carRentals.noClassical, las=2)
```

##### <span style="color: Teal;"> *2.4.1.3 Regression of log.rate.daily ~ vehicle.make* </span>

```{r}
lm.fit <- lm(log.rate.daily ~ vehicle.make, data=carRentals.noClassical)
summary(lm.fit)
```

```{r}
mse.usd(lm.fit)
```

```{r}
summary(aov(log.rate.daily ~ vehicle.make, data=carRentals.noClassical))
```

vehicle.make is a significantly explanative feature

#### <span style="color: #FFBF00;"> *2.4.2 Relationship of log.rate.daily ~ vehicle.model* </span>

##### <span style="color: Teal;"> *2.4.2.1 Problems with vehicle.model data* </span>

**Concilliation of Multi-spelled models**

Model variable requires consolidation if it is to be used properly.

```{r}
print(carRentals.noClassical %>% count(vehicle.model))
```

##### <span style="color: Teal;"> *2.4.2.2 Reconciliation of multi-spelled car model with the most commonly spelled version* </span>

```{r}
models.to.change <- c("2-Series", "3-Series", "4-Series", "488 Gtb", "5-Series", "7-Series", "Accord Hybrid", "Accord Sedan", "Avalon Hybrid", "C-Max Hybrid", "Camry Hybrid", "Civic Sedan", "Corolla Hybrid", "e-Golf", "E-Golf", "F-Type", "Fusion Hybrid", "I3", "I8", "RAV4 Hybrid", "Silverado 1500 Hybrid", "Soul EV", "Tahoe Hybrid", "X5 eDrive")
models.references <- c("2 Series", "3 Series", "4 Series", "488GTB", "5 Series", "7 Series", "Accord", "Accord", "Avalon", "C-Max", "Camry", "Civic", "Corolla", "Golf", "Golf", "F-TYPE", "Fusion", "i3", "i8", "RAV4", "Silverado 1500", "Soul", "Tahoe", "X5")
```

```{r}
for(i in 1:length(models.to.change)) {
  models.to.change.rows <- carRentals.noClassical[carRentals.noClassical$vehicle.model == models.to.change[i],]
  for(j in 1:nrow(models.to.change.rows)) {
    row.temp <- models.to.change.rows[j,]
    carRentals.noClassical[row.names(row.temp), "vehicle.model"] <- models.references[i]
  }
}
```

Confirm successful reconciliation of makes

```{r}
carRentals.noClassical %>% count(vehicle.model)
```

Reset factors

```{r}
carRentals.noClassical$vehicle.model <- droplevels(carRentals.noClassical$vehicle.model)
```

```{r}
options(repr.plot.width=15, repr.plot.height=10)
par(mfrow=c(2,1))
boxplot(carRentals.noClassical$log.rate.daily ~ vehicle.model, data=carRentals.noClassical, las=2)
plotmeans(log.rate.daily ~ vehicle.model, data=carRentals.noClassical, las=2)
```

##### <span style="color: Teal;"> *2.4.2.3 Regression of log.rate.daily ~ vehicle.model* </span>

```{r}
lm.fit <- lm(log.rate.daily ~ vehicle.model, data=carRentals.noClassical)
summary(lm.fit)
```

```{r}
mse.usd(lm.fit)
```

```{r}
summary(aov(log.rate.daily ~ vehicle.model, data=carRentals.noClassical))
```

#### <span style="color: #FFBF00;"> *2.4.3 Relationship of log.rate.daily ~ fuelType* </span>

##### <span style="color: Teal;"> *2.4.3.1 Problems with fuelType data* </span>

```{r}
unique(carRentals.noClassical$fuelType)
```

```{r}
table(carRentals.noClassical$fuelType)
```

```{r}
na.fuel.rows <- carRentals.noClassical[carRentals.noClassical$fuelType == "",][,c("vehicle.make", "vehicle.model", "vehicle.year")]
unique(na.fuel.rows)
```

```{r}
options(repr.plot.width=8, repr.plot.height=5)
boxplot(carRentals.noClassical$log.rate.daily ~ fuelType, data=carRentals.noClassical)
```

```{r}
options(repr.plot.width=5, repr.plot.height=4)
hist(unique(na.fuel.rows)$vehicle.year, breaks=(max(unique(na.fuel.rows$vehicle.year))-min(unique(na.fuel.rows$vehicle.year))+1))
```

Exploring an example below, a lot of car models with missing fuelType have other entries with existing values

```{r}
carRentals.noClassical[carRentals.noClassical$vehicle.make == "Toyota" &
    carRentals.noClassical$vehicle.model == "Camry" &
    carRentals.noClassical$vehicle.year == 2020,]
```

##### <span style="color: Teal;"> *2.4.3.2 Imputation of missing fuelType's ~ fuelType* </span>

**Impute missing fuelType with the most common one for each type (*type: c(make,model,year)*)**

```{r}
global.fuel.mode <- as.character(Mode(carRentals.noClassical$fuelType))
```

```{r}
carRentals.noClassical[rownames(na.fuel.rows),]
```

```{r}
for(i in 1:nrow(na.fuel.rows)) {
  row.temp <- na.fuel.rows[i,]
  df.temp <- carRentals.noClassical[carRentals.noClassical$vehicle.make == row.temp$vehicle.make &
    carRentals.noClassical$vehicle.model == row.temp$vehicle.model &
    carRentals.noClassical$vehicle.year == row.temp$vehicle.year &
    carRentals.noClassical$fuelType != "",]
  mode.temp <- as.character(Mode(df.temp$fuelType))
  if(is.na(mode.temp) | mode.temp =="") {
    mode.temp <- global.fuel.mode
  }
  carRentals.noClassical[row.names(row.temp), "fuelType"] <- mode.temp
}
```

```{r}
carRentals.noClassical[carRentals.noClassical$vehicle.make == "Toyota" &
    carRentals.noClassical$vehicle.model == "Camry" &
    carRentals.noClassical$vehicle.year == 2020,]
```

Confirm successful filling of empty fuelType cells

```{r}
table(carRentals.noClassical$fuelType)
```

Reset factors to drop empty ""

```{r}
carRentals.noClassical$fuelType <- droplevels(carRentals.noClassical$fuelType)
```

```{r}
table(carRentals.noClassical$fuelType)
```

```{r}
options(repr.plot.width=12, repr.plot.height=5)
par(mfrow=c(1,2))
boxplot(carRentals.noClassical$log.rate.daily ~ fuelType, data=carRentals.noClassical)
plotmeans(log.rate.daily ~ fuelType, data=carRentals.noClassical)
```

##### <span style="color: Teal;"> *2.4.3.3 Regression of log.rate.daily ~ fuelType* </span>

```{r}
lm.fit <- lm(log.rate.daily ~ fuelType, data=carRentals.noClassical)
summary(lm.fit)
```

```{r}
mse.usd(lm.fit)
```

```{r}
mae.usd(lm.fit)
```

```{r}
summary(aov(log.rate.daily ~ fuelType, data=carRentals.noClassical))
```

fuelType is a significantly explanative feature

#### <span style="color: #FFBF00;"> *2.4.4 Relationship of log.rate.daily ~ vehicle.type* </span>

```{r}
unique(carRentals.noClassical$vehicle.type)
```

```{r}
table(carRentals.noClassical$vehicle.type)
```

```{r}
options(repr.plot.width=12, repr.plot.height=5)
par(mfrow=c(1,2))
boxplot(carRentals.noClassical$log.rate.daily ~ vehicle.type, data=carRentals.noClassical)
plotmeans(log.rate.daily ~ vehicle.type, data=carRentals.noClassical)
```

```{r}
lm.fit <- lm(log.rate.daily ~ vehicle.type, data=carRentals.noClassical)
summary(lm.fit)
```

```{r}
summary(aov(log.rate.daily ~ vehicle.type, data=carRentals.noClassical))
```

vehicle.type is a significantly explanative feature

### <span style="color: LightSalmon;"> *2.5 Creation of New Features* </span>

#### <span style="color: #FFBF00;"> *2.5.1 city.has.airport <- location.city==airportcity* </span>

```{r}
carRentals.noClassical$city.has.airport <- as.character(carRentals.noClassical$location.city) == as.character(carRentals.noClassical$airportcity)
```

```{r}
table(carRentals.noClassical$city.has.airport)
```

```{r}
options(repr.plot.width=12, repr.plot.height=5)
par(mfrow=c(1,2))
boxplot(carRentals.noClassical$log.rate.daily ~ city.has.airport, data=carRentals.noClassical)
plotmeans(log.rate.daily ~ city.has.airport, data=carRentals.noClassical)
```

```{r}
lm.fit <- lm(log.rate.daily ~ city.has.airport, data=carRentals.noClassical)
summary(lm.fit)
```

```{r}
mse.usd(lm.fit)
```

city.has.airport is a significantly explanative feature

## <span style="color: IndianRed;"> 3. Modelling </span>

#### <span style="color: LightSalmon;"> *3.1 Develop overall Linear Regression Model* </span>

##### <span style="color: Teal;"> *3.1.1 Fit Linear Regression Model with All Numerical Features* </span>

```{r}
full.model <- lm(log.rate.daily ~ vehicle.year + rating + reviewCount + renterTripsTaken, data=carRentals.noClassical)
summary(full.model)
```

```{r}
mse.usd(full.model)
```

##### <span style="color: Teal;"> *3.1.2 Fit Linear Regression Model with All Categorical Features* </span>

**With make, without model**

```{r}
full.model <- lm(log.rate.daily ~ fuelType + vehicle.type + city.has.airport + vehicle.make, data=carRentals.noClassical)
summary(full.model)
```

```{r}
mse.usd(full.model)
```

**With model, without make**

```{r}
full.model <- lm(log.rate.daily ~ fuelType + vehicle.type + city.has.airport + vehicle.model, data=carRentals.noClassical)
summary(full.model)
```

```{r}
mse.usd(full.model)
```

**With both model and make**

```{r}
full.model <- lm(log.rate.daily ~ fuelType + vehicle.type + city.has.airport + vehicle.make + vehicle.model, data=carRentals.noClassical)
summary(full.model)
```

```{r}
mse.usd(full.model)
```

##### <span style="color: Teal;"> *3.1.3 Fit Linear Regression Model with All Chosen Features* </span>

**With both make and model**

```{r}
full.model <- lm(log.rate.daily ~ vehicle.year + rating + reviewCount + renterTripsTaken +
    fuelType + vehicle.type + city.has.airport + vehicle.make + vehicle.model, data=carRentals.noClassical)
summary(full.model)
```

```{r}
mse.usd(full.model)
```

**With make, without model**

```{r}
full.model <- lm(log.rate.daily ~ vehicle.year + rating + reviewCount + renterTripsTaken +
    fuelType + vehicle.type + city.has.airport + vehicle.make, data=carRentals.noClassical)
summary(full.model)
```

```{r}
mse.usd(full.model)
```

**Without make, with model**

```{r}
full.model <- lm(log.rate.daily ~ vehicle.year + rating + reviewCount + renterTripsTaken +
    fuelType + vehicle.type + city.has.airport + vehicle.model, data=carRentals.noClassical)
summary(full.model)
```

```{r}
mse.usd(full.model)
```

```{r}
options(repr.plot.width=12, repr.plot.height=12)
par(mfrow=c(2,2))
plot(full.model)
```

##### <span style="color: Teal;"> *3.1.2 Check Multicolliniarity* </span>

```{r}
names(full.model)
```

**Identify dummy variables that cause multicollineariy issue**

```{r}
alias(full.model)
```

Our set of features suffer from multicollinearity problem. <br>Stepwise feature selection will be applied to eliminate least explanative features in hope of reducing the muticollinearity problem.

##### <span style="color: Teal;"> *3.1.3 Stepwise Linear Regression Model* </span>

```{r}
step.model <- stepAIC(full.model, direction="both", trace=FALSE, k=20)
summary(step.model)
```

```{r}
mse.usd(step.model)
```

A comparable Adjusted R<sup>2</sup> is achieved (0.5864 vs 0.5880) even when fuelType, reviewCount, and retnerTripsTaken are dropped.

```{r}
vif(step.model)
```

```{r}
sqrt(vif(step.model))
```

The stepwise linear regression model no longer suffers from a multicollinearity problem as none of the features in  have sqrt(VIF) > 2

#### <span style="color: LightSalmon;"> *3.2 Diagnostics* </span>

```{r}
summary(full.model$residuals)
```

```{r}
summary(step.model$residuals)
```

```{r}
shapiro.test(sample(full.model$residuals, 2000, replace=FALSE))
```

```{r}
shapiro.test(sample(step.model$residuals, 2000, replace=FALSE))
```

```{r}
options(repr.plot.width=5, repr.plot.height=4)
ggqqplot(full.model$residuals)
```

```{r}
options(repr.plot.width=5, repr.plot.height=4)
ggqqplot(step.model$residuals)
```

```{r}
ggdensity(full.model$residuals, fill="lightgray", title="Residuals") +
  stat_overlay_normal_density(color = "red", linetype = "dashed")
```

```{r}
ggdensity(step.model$residuals, fill="lightgray", title="Residuals") +
  stat_overlay_normal_density(color = "red", linetype = "dashed")
```

```{r}
options(repr.plot.width=15, repr.plot.height=6)
ols_plot_resid_stand(full.model)
```

```{r}
ols_plot_resid_stand(step.model)
```

##### <span style="color: Teal;"> *3.2.1 Robust Linear Regression Model* </span>

### <span style="color: Salmon;"> *4 Regression Tree* </span>

##### <span style="color: Teal;"> *4.1 Building the Regression tree* </span>

```{r}
cr_noclassical <- select(carRentals.noClassical, rate.daily, fuelType, rating, renterTripsTaken, reviewCount, vehicle.year, vehicle.type)
```

```{r}
set.seed(1000)
```

```{r}
sample_cr <- sample.split(cr_noclassical$rate.daily, SplitRatio = .70)
```

```{r}
train_cr = subset(cr_noclassical, sample_cr ==TRUE)
test_cr = subset(cr_noclassical, sample_cr == FALSE)
```

```{r}
rtree <- rpart(rate.daily~., data = cr_noclassical, cp=0.001)
printcp(rtree)
```

```{r}
rpart.plot(rtree, cex=0.45)
```

The three significant features are: Fuel Type, Rating and Vehicle Year (in that order).

```{r}
cr_noclassicalii <- select(carRentals.noClassical, rate.daily, fuelType, rating, renterTripsTaken, reviewCount, vehicle.year, vehicle.type, vehicle.model, vehicle.make)
```

```{r}
cr_noclassicalii <- cr_noclassicalii[!is.na(cr_noclassicalii$rating),]
```

```{r}
sample_crii <- sample.split(cr_noclassicalii, SplitRatio = .70)
```

```{r}
train_crii = subset(cr_noclassicalii, sample_crii ==TRUE)
test_crii = subset(cr_noclassicalii, sample_crii == FALSE)
```

```{r}
rfii <- randomForest(rate.daily~. -vehicle.model -vehicle.make, data = train_crii, importance = TRUE)
```

```{r}
varImpPlot(rfii)
```

fuelType plays an important role in our model